PDBF Documentation

### 2015-06-03 Documentation.tex
added minimal ui for multiplot

\option
{topArr}
{Sets the labels for the tod side.}
{Either a JavaScript array of Strings where each string corresponds to exactly one column (e.g \{"column1", "column2"\}) or a JavaScript array of Objects with a c property which corresponds to the number of columns this text should span and a text property which corresponds to the text-string.}
{If this option is not set, then the value that is used for the query in this column is used.}

>>>>

\option
{topArr}
{Sets the labels for the top side.}
{Either a JavaScript array of Strings where each string corresponds to exactly one column (e.g \{"column1", "column2"\}) or a JavaScript array of Objects with a c property which corresponds to the number of columns this text should span and a text property which corresponds to the text-string.}
{If this option is not set, then the value that is used for the query in this column is used.}
